---
title: "Data_Wrangling_2"
output: github_document
---


```{r}
library(tidyverse)
library(rvest)
library(httr)
```

### NSDUH Data

```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

drug_use_html = read_html(url)

```

```{r}
drug_use_html %>%
  html_table() %>%
  first() %>%
  slice(-1) %>% view
```


### Star Wars

```{r}
sw_url = "https://www.imdb.com/list/ls070150896/"

sw_html = read_html(sw_url)

sw_titles= 
  sw_html %>%
  html_elements(".lister-item-header a") %>%
  html_text

gross_rev_vec = 
  swm_html %>%
  html_elements(".text-small:nth-child(7) span:nth-child(5)") %>%
  html_text()

swm_df =
  tibble(
    title = sw_titles,
    rev = gross_rev_vec
  )
```


#### Napoleon Dynamite

Reviews

```{r}
dynamite_url = url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(dynamite_url)

review_titles = 
  dynamite_html %>%
  html_elements(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_elements("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = 
  dynamite_html %>%
  html_elements(".review-text-content span") %>%
  html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
